% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[A4paper,11pt]{article}


%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\usepackage{amsmath,xspace}
\definecolor{mygrey}{gray}{0.90}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\large Govind C}  & +91-8682927216/9947879879 (mobile)\\
Room no:316,Jamuna Hostel &  govindc27@gmail.com\\
IITM,Chennai-36,India & \textbf{Roll No:CS13M020} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{M.Tech-Indian Institute of Technology, Madras}{\url{http://www.iitm.ac.in}}{Computer Science \& Engineering. CGPA 7 on a scale of 10}{2013-Present}
\item
	\ressubheading{B.Tech-MES College of Engineering-University of Calicut}{\url{http://www.mesce.ac.in}}{Information Technology. Percentage-59.42}{Class of 2012}

\item
	\ressubheading{XII-Govt. MBHSS, Kunnamkulam}{\url{modelboyshsskkm.blogspot.in}}{Computer Science Group Kerala State Board. Percentage-73.50}{Class of 2007}
\item
	\ressubheading{X-Bethany St.Johns HSS, Kunnamkulam}{\url{http://bethanystjohns.edu.in}}{SSLC Kerala State Board. Percentage-89.47}{Class of 2005}
\end{itemize}

\resheading{Professional Experience}
\begin{itemize}
\item
	\ressubheading{ZimmerSOFT, \url{http://zimmersoft.com/}}{Cochin, Kerala, India}{Junior Programmer}{January,2013-July,2013}
	\begin{itemize}
		\item{Worked in two projects in Python/Django}
		\resitem[1]{An intern-ship portal for start-up client based out in US.}
		\resitem[2]{A recruitment solution website for client based out in US.}
	\end{itemize}
\end{itemize}

\resheading{Relevant Coursework}
\begin{description}
\item[Computer Science:]
Advanced Algorithms
Knowledge Representation and Reasoning,
Digital System Testing and Testable Design,
Computer Architecture.
\item[Information Technology:]
Information Retrieval,
Advanced Database Management System,
Digital Data Communication.
\end{description}

\resheading{Projects}
\begin{itemize}

\item
	\ressubheading{Algorithms \& Hardness for computing the rotation distance of the binary tree}{IITM}{Guide-Dr.Jayalal Sarma,Asst. Professor}{Algorithms}
	\begin{itemize}
		\item{Rotation Distance is minimal number of rotations needed to transform one tree into another of same size. Rotations provide a simple mechanism for balancing trees while preserving their underlying order. There are no known polynomial-time algorithms for computing rotation distance,thus trying to formulate an algorithm with better bound and possible implementation.}
		\resitem{ Ongoing.}
	\end{itemize}
	
\item	
	\ressubheading{Malayalam to CD theory conversion}{IIT Madras}{Instructor-Dr.Deepak Khemani,Professor}{Knowledge Representation \& Reasoning}
	\begin{itemize}
		\item{The CD theory defines a semantic base for knowledge representation. It aims at understanding natural language stories. We selected Indian General Election 2014 as domain. Created a parser for processing malayalam sentences and convert it to CD representation which in turn can be converted into any other languages. Implemented using Java.}
		\resitem{\url{https://github.com/amigozgovi/malayalamToCd}}
	\end{itemize}
	
\item	
	\ressubheading{GIT+ - porting projects to Git}{MESCE,University of Calicut}{Guide-Dr.C.K.Raju,HOD IT Dept.}{Version Control System}
	\begin{itemize}
		\item{We developed a tool to support portability across version control systems specifically to Git. Core idea was to transform from formats associated to other version control systems to that of Git. The implementation was in C++ .}
		\resitem{\url{https://github.com/amigozgovi/gitplus}}
	\end{itemize}
	
\item	
	\ressubheading{AGROTECH- a website on agriculture}{MESCE-University of Calicut}{Guide-Jasmin.T.Jose, Asst.Professor,IT Dept.}{Web}
	\begin{itemize}
		\item{An interactive website designed using HTML,CSS and implemented using PHP,MySQL database(WAMP Server bundle). Aim was to develop a platform to promote IT in agriculture, assist one in getting or sharing information or service on agriculture she or he wants. Started for one village, but has the capability to scale to more upon need.}
		\resitem{\url{https://github.com/amigozgovi/agrotech}}
	\end{itemize}
\end{itemize}

\resheading{Technical Skills}

\begin{description}
\item[Tools \& Languages:]  C/C++, Python/Django, PHP, GIT, Latex, Java, Javascript, Shell, HTML, CSS, Joomla, Eclipse, Sublime Text, GNUplot, GNUmake, Valgrind, Doxygen.
\item[Operating Systems:] Unix/Linux based OS's, Windows 98/XP/Vista.
\end{description}

\resheading{Awards and Achievements}
	\begin{description}
		\resitem[2005] Received Rashtrapthi Scout award from the President of India.
		\resitem[2005-07]Played in HSS Basket Ball team \& Runners in district level basket ball tournament.
		\resitem[2013] Gate Examination All India Rank:\textbf{595}.
\end{description}

\resheading{Position of Responsibility}
\begin{description}
\item[Troop Leader:] Club/Scout-$47^{th}$ Scout Troop-Bethany HSS.
\item[Secretary:] Association-Students Association of IT, MESCE.
\item[Volunteer:] Conference-WALCOM 2014 Eighth International workshop on Algorithms and computation.
\end{description}

\resheading{Interests and Hobbies}
\begin{description}
\item[Health:]
Running, Swimming, Bicycling, Basketball
\item[Books:]
Automobile Magazines
\item[Gadget \& Technologies:]
Linux, Android, Smart phones
\item[Others:]
Internet, Music, Movies, Events
\end{description}

\resheading{Personal Information}
\begin{description}
\resitem[Gender/Nationality:]Male/Indian.
\resitem[DOB:]30-December-1989.
\resitem[Permanent Address:]GovindVihar, Chalissery PO, Palakkad, Kerala-679536, India.
\resitem[Phone:]+91-466-2256162.
\end{description}

\resheading{Declaration}
\begin{description}
\item{I hereby declare that the information furnished above is true to the best of my knowledge.}
\end{description}

\end{document}