% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[A4paper,11pt]{article}


%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\usepackage{amsmath,xspace}
\definecolor{mygrey}{gray}{0.90}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\large Govind C}  & +91-8682927216/9947879879 (mobile)\\
\textbf{Present:}Room no:316, Jamuna Hostel, IITM, Chennai-36, TN, India  &  govindc27@gmail.com\\
\textbf{Home:}GovindVihar, Chalissery PO, Palakkad, Kerala-679536, India & \textbf{Roll No:CS13M020} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{M.Tech-Indian Institute of Technology, Madras}{\url{http://www.iitm.ac.in}}{Computer Science \& Engineering stream. CGPA 7}{2013-Present}
\item
	\ressubheading{B.Tech-MES College of Engineering-University of Calicut}{\url{http://www.mesce.ac.in}}{Information Technology stream. Percentage-59.42}{Class of 2012}
\end{itemize}

\resheading{Professional Experience}
\begin{itemize}
\item
	\ressubheading{ZimmerSOFT, \url{http://zimmersoft.com/}}{Cochin, Kerala, India}{Junior Programmer}{January,2013-July,2013}
	\begin{itemize}
		\item{Worked in two projects in Python/Django.}
	\end{itemize}
\end{itemize}

%\resheading{Relevant Coursework}
%\begin{description}
%\item[Computer Science:]
%Advanced Data structure and algorithm,
%Advanced Algorithms,
%Knowledge Representation and Reasoning,
%Digital System Testing and Testable Design,
%Computer Architecture,
%Cryptography and Network Security.
%\item[Information Technology:]
%Information Retrieval,
%Management Information System,
%Advanced Database Management System,
%Digital Data Communication.
%\end{description}

\resheading{Projects}
\begin{itemize}

\item
	\ressubheading{Algorithms \& Hardness for computing the rotation distance of the binary tree}{IITM}{Guide-Dr.Jayalal Sarma,Asst. Professor}{Algorithms}
	\begin{itemize}
		\item{There are no known polynomial-time algorithms for computing rotation distance,thus trying to formulate an algorithm with better bound and possible implementation. Ongoing.}
	\end{itemize}
	
\item	
	\ressubheading{Malayalam to CD theory conversion}{IIT Madras}{Instructor-Dr.Deepak Khemani,Professor}{Knowledge Representation \& Reasoning}
	\begin{itemize}
		\item{Created a parser for processing malayalam sentences and convert it to CD,a semantic base for knowledge representation. Implemented using Java.}
		\resitem{\url{https://github.com/amigozgovi/malayalamToCd}}
	\end{itemize}
	
\item	
	\ressubheading{GIT+ - porting projects to Git}{MESCE,University of Calicut}{Guide-Dr.C.K.Raju,HOD IT Dept.}{Version Control System}
	\begin{itemize}
		\item{A tool to transform from formats associated to other version control systems to that of Git. Implemented using C++.}
		\resitem{\url{https://github.com/amigozgovi/gitplus}}
	\end{itemize}
	
\item	
	\ressubheading{AGROTECH- a website on agriculture}{MESCE-University of Calicut}{Guide-Jasmin.T.Jose, Asst.Professor,IT Dept.}{Web}
	\begin{itemize}
		\item{A interactive website using PHP,MySQL,HTML,CSS \& WAMP Server bundle.}
		\resitem{\url{https://github.com/amigozgovi/agrotech}}
	\end{itemize}
\end{itemize}

\resheading{Technical Skills}

\begin{description}
\item[Tools \& Languages:]  C/C++, Python/Django, PHP, Latex, Java, Javascript, Shell, HTML, CSS, Joomla, Eclipse, Sublime Text, GNUplot, GNUmake, Valgrind, Doxygen.
\end{description}

\resheading{Achievements}
	\begin{description}
		\resitem[2013] Gate Examination All India Rank:\textbf{595}.
\end{description}

\resheading{Positions of Responsibility}
\begin{description}
\item[Troop Leader] Club/Scout-$47^{th}$ Scout Troop-Bethany HSS. Received President Scout Award. 
\item[Volunteer] Conference-WALCOM 2014 Eighth International workshop on Algorithms and computation.
\end{description}

\resheading{Declaration}
\begin{description}
\item{I hereby declare that the information furnished above is true to the best of my knowledge.}
\end{description}

\end{document}

